Computing astrophysical inferences with diffusive nested sampling

### 2014-03-23 ms.tex
Added Neal references
massinf

Recently we investigated a Bayesian approach for finding objects in ``crowded
fields'', small patches of the sky where many stars are visible in an image.
Each star would appear as a point source in the image, except for the effects
of blurring (caused by either diffraction as the light enters the telescope,
or by atmospheric fluctuations), and the images are also typically noisy.
Since the number of stars $N$ is itself unknown, we use reversible jump
MCMC {\it within} DNS to infer $N$.

@@

>>>>

Recently we investigated a Bayesian approach for finding objects in ``crowded
fields'', small patches of the sky where many stars are visible in an image.
Each star would appear as a point source in the image, except for the effects
of blurring (caused by either diffraction as the light enters the telescope,
or by atmospheric fluctuations), and the images are also typically noisy.
Since the number of stars $N$ is itself unknown, we use reversible jump
MCMC {\it within} DNS to infer $N$. The model assumptions here are very similar
to those suggested in \citep{massinf} for inferring positive additive
distributions, but here the assumption that the underlying scene is composed
of point sources is well justified, rather than a convenience.

@@

\bibitem[Neal(1998)]{ais} Neal, R.~M.\ 1998.\ Annealed 
Importance Sampling.\ ArXiv Physics e-prints arXiv:physics/9803008.

\bibitem[Neal(2005)]{lis} Neal, R.~M.\ 2005.\ Estimating 
Ratios of Normalizing Constants Using Linked Importance Sampling.\ ArXiv 
Mathematics e-prints arXiv:math/0511216.

\bibitem[Skilling(1998)]{massinf} Skilling, J.\ 1998.\ Massive 
Inference and Maximum Entropy.\ Maximum Entropy and Bayesian Methods, 1.
